Jack Antonoff-ification of pop music

### 2023-04-04 outputs/paper/paper.qmd
got the graphs to render

```{r}
#| label: fig-energy
#| fig-cap: Energy Variable
#| echo: false
# 
# library(lubridate)
# df <- read.csv(here::here("inputs/data/df.csv"))
# df %>%
#   filter(album_release_date_precision == "day") %>%
#   mutate(album_release_date = ymd(album_release_date)) %>%
#   ggplot(aes(y = energy, x = album_release_date, color = jack)) +
#   geom_point() +
#   theme_minimal() +
#   scale_color_manual(values = c("#FFB6C1", "#808080")) +
#   labs(color = "Has 'y' in jack?") +
#   facet_wrap(~ artist_name, ncol = 3)

@@

# df %>%
#   filter(album_release_date_precision == "day") %>%
#   mutate(album_release_date = ymd(album_release_date)) %>%
#   ggplot(aes(y = danceability, x = album_release_date, color = jack)) +
#   geom_point() +
#   theme_minimal() +
#   scale_color_manual(values = c("#FFB6C1", "#808080")) +
#   labs(color = "Has 'y' in jack?") +
#   facet_wrap(~ artist_name, ncol = 3)

@@

# df %>%
#   filter(album_release_date_precision == "day") %>%
#   mutate(album_release_date = ymd(album_release_date)) %>%
#   ggplot(aes(y = valence, x = album_release_date, color = jack)) +
#   geom_point() +
#   theme_minimal() +
#   scale_color_manual(values = c("#FFB6C1", "#808080")) +
#   labs(color = "Has 'y' in jack?") +
#   facet_wrap(~ artist_name, ncol = 3)

@@

# df %>%
#   filter(album_release_date_precision == "day") %>%
#   mutate(album_release_date = ymd(album_release_date)) %>%
#   ggplot(aes(y = acousticness, x = album_release_date, color = jack)) +
#   geom_point() +
#   theme_minimal() +
#   scale_color_manual(values = c("#FFB6C1", "#808080")) +
#   labs(color = "Has 'y' in jack?") +
#   facet_wrap(~ artist_name, ncol = 3)

@@

# 
# df %>%
#   filter(album_release_date_precision == "day") %>%
#   mutate(album_release_date = ymd(album_release_date)) %>%
#   ggplot(aes(y = instrumentalness, x = album_release_date, color = jack)) +
#   geom_point() +
#   theme_minimal() +
#   scale_color_manual(values = c("#FFB6C1", "#808080")) +
#   labs(color = "Has 'y' in jack?") +
#   facet_wrap(~ artist_name, ncol = 3)

@@

```{r}
#| label: fig-tempo
#| fig-cap: Tempo Variable
#| echo: false

# 
# df %>%
#   filter(album_release_date_precision == "day") %>%
#   mutate(album_release_date = ymd(album_release_date)) %>%
#   ggplot(aes(y = tempo, x = album_release_date, color = jack)) +
#   geom_point() +
#   theme_minimal() +
#   scale_color_manual(values = c("#FFB6C1", "#808080")) +
#   labs(color = "Has 'y' in jack?") +
#   facet_wrap(~ artist_name, ncol = 3)

>>>>

```{r}
#| label: fig-energy
#| fig-cap: Energy Variable
#| echo: false

library(lubridate)
df <- read.csv(here::here("inputs/data/df.csv"))
df$jack <- factor(df$jack)
df %>%
  filter(album_release_date_precision == "day") %>%
  mutate(album_release_date = ymd(album_release_date)) %>%
  ggplot(aes(y = energy, x = album_release_date, color = jack)) +
  geom_point() +
  theme_minimal() +
  scale_color_manual(values = c("#808080","#FFB6C1")) +
  labs(color = "Has 'y' in jack?") +
  facet_wrap(~ artist_name, ncol = 3)

@@

df %>%
  filter(album_release_date_precision == "day") %>%
  mutate(album_release_date = ymd(album_release_date)) %>%
  ggplot(aes(y = danceability, x = album_release_date, color = jack)) +
  geom_point() +
  theme_minimal() +
  scale_color_manual(values = c("#808080","#FFB6C1")) +
  labs(color = "Has 'y' in jack?") +
  facet_wrap(~ artist_name, ncol = 3)

@@

df %>%
  filter(album_release_date_precision == "day") %>%
  mutate(album_release_date = ymd(album_release_date)) %>%
  ggplot(aes(y = valence, x = album_release_date, color = jack)) +
  geom_point() +
  theme_minimal() +
  scale_color_manual(values = c("#808080","#FFB6C1")) +
  labs(color = "Has 'y' in jack?") +
  facet_wrap(~ artist_name, ncol = 3)

@@

df %>%
  filter(album_release_date_precision == "day") %>%
  mutate(album_release_date = ymd(album_release_date)) %>%
  ggplot(aes(y = acousticness, x = album_release_date, color = jack)) +
  geom_point() +
  theme_minimal() +
  scale_color_manual(values = c("#808080","#FFB6C1")) +
  labs(color = "Has 'y' in jack?") +
  facet_wrap(~ artist_name, ncol = 3)

@@

df %>%
  filter(album_release_date_precision == "day") %>%
  mutate(album_release_date = ymd(album_release_date)) %>%
  ggplot(aes(y = instrumentalness, x = album_release_date, color = jack)) +
  geom_point() +
  theme_minimal() +
  scale_color_manual(values = c("#808080","#FFB6C1")) +
  labs(color = "Has 'y' in jack?") +
  facet_wrap(~ artist_name, ncol = 3)

@@

#| label: fig-temp
#| fig-cap: Tempo Variable
#| echo: false

df %>%
  filter(album_release_date_precision == "day") %>%
  mutate(album_release_date = ymd(album_release_date)) %>%
  ggplot(aes(y = tempo, x = album_release_date, color = jack)) +
  geom_point() +
  theme_minimal() +
  scale_color_manual(values = c("#808080","#FFB6C1")) +
  labs(color = "Has 'y' in jack?") +
  facet_wrap(~ artist_name, ncol = 3)
